%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume
\documentclass[margin, line]{resume}

\setlength{\topmargin}{ -8 mm}  
\setlength{\oddsidemargin}{-0.75in} 
%\setlength{\evensidemargin}{2in} 
\setlength{\textwidth}{6.65 in}
\setlength{\textheight}{10.9 in} 
\usepackage{url}
\urlstyle{same}
%______________________________________________________________________________________________________________________
\begin{document}
\name{\centering{\large{Devin A. Bonnie }}  \hspace{96mm} \small{ \url{www.linkedin.com/in/devinbonnie/} } } 
\begin{resume}
\vspace{-2mm}
%__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact}

	718 Old San Francisco Road, \#329		  \hfill devin.bonnie@gmail.com \\ \vspace{-2mm}%
	Sunnyvale, CA 94086                           \hfill   (810)623--2687 \vspace{0mm}\vspace{-2mm}%
    %__________________________________________________________________________________________________________________
    % Objective
    \section{\mysidestyle Profile}
   
Engineer with experience in operational robotics, software architecture design, stochastic systems, computer vision, and embedded systems. Knowledgeable concerning system design, from low- to high-level.  \vspace{-4mm}
%%__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textbf{University of Illinois at Urbana-Champaign}, Illinois  \hfill GPA: 3.66 \vspace{0mm}\\%
    \textsl{M.S., Electrical and Computer Engineering} \hfill \textsl{Sept. 2009 -- Dec. 2011}\\
    \textsl{Advisor:} S.A. Hutchinson \vspace{-2mm} %

    \textbf{Hope College}, Michigan  \hfill GPA: 3.41\vspace{0mm}\\%
    \textsl{B.S., Engineering (Electrical Emphasis), Cum Laude; Mathematics Minor} \hfill \textsl{Jan. 2004 -- Dec. 2007}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Senior project recognized with the \textit{VanPutten Engineering Design Award}.
    \end{list2}\vspace{-2mm}

    %__________________________________________________________________________________________________________________
    % Experience
    \section{\mysidestyle Experience}
   
    \textbf{Regulus Team} \hfill Senior Software Engineer\\  
    Liquid Robotics \hfill \textsl{May 2014 -- Present} \\
    \vspace{ -2 mm}
    \begin{list2}
        \item Regulus project lead and full-stack engineer that defines requirements, identifies key features, quantifies customer needs, and plans release schedules
        \item Core responsibilities include navigation, device drivers, WebUI, and communications protocol architecture
        \item Operations support lead, routinely diagnose and apply root cause analysis to customer-facing issues
        \item Implemented live, hurricane-tweeting drone that generated national news.
    \end{list2}\vspace{-2mm}

    \textbf{Platform / Data Services Team} \hfill Software Engineer\\  
    Liquid Robotics \hfill \textsl{Aug. 2012 -- Apr. 2014} \\
    \vspace{ -2 mm}
    \begin{list2}
        \item Platform contributions included work on core vehicle components, e.g., navigation, communications.
        \item Integrated multiple sensors for SV2 and SV3 platforms, e.g., cameras, gps, weather, oceanographic.
    \end{list2}\vspace{-2mm}

    \textbf{ISDA Group} \hfill Research Programmer\\  
    National Center for Supercomputing Applications \hfill \textsl{Oct. 2011 -- Jul. 2012} \\
    \vspace{ -2 mm}
    \begin{list2}
        \item Responsibilities included image comparison techniques, data visualization, and automated decision support. 
        \item Other tasks included efficient incorporation/rendering of 3-D image data over lossy network streams.  
    \end{list2}\vspace{-2mm}
   
    \textbf{Software Technology Group} \hfill Intern\\  
    Wolfram Research, Inc. \hfill \textsl{May 2011 -- Sept. 2011} \\
    \vspace{ -2 mm}
    \begin{list2}
        \item Contributed to a developmental C++ API for both implementation and specification.
	 \item Accomplished reliable communication, file I/O, and robust sensor measurement methods. 
    \end{list2}\vspace{-2mm}

    \textbf{Dept. of Electrical and Computer Engineering} \hfill Teaching Assistant/Research Assistant \\  
    University of Illinois at Urbana-Champaign \hfill \textsl{Jan. 2010 -- Aug. 2011} \\
    \vspace{ -2 mm}
    \begin{list2}
        \item Modelled Bayesian search using properties of the exponential family and regularized particle filtering.
	 \item Thesis work resulted in an IEEE conference publication (appeared in the May 2012 ICRA proceedings).  
        \item Assisted and lectured in senior and undergraduate courses covering robotics and circuit design.
    \end{list2}\vspace{-2mm}

    \textbf{Research and Development Division} \hfill Summer Fellow \\ 
    Monterey Bay Aquarium Research Institute \hfill \textsl{Jun. 2009 -- Sept. 2009}  \\
    \vspace{ -2 mm}	
    \begin{list2}
	\item Contributed to the `Software Infrastructure and Applications for MOOS' (SIAM) Java API. 
	\item Developed new SIAM software instrumentation drivers and sampling protocols.
	\item Configured embedded controllers with various Linux kernels and JVMs for evaluation.
    \end{list2}\vspace{-2mm}
    
    \textbf{Great Lakes Environmental Research Laboratory } \hfill  Research Assistant \\ 
	National Oceanic and Atmospheric Administration \hfill \textsl{Mar. 2009 -- Jun. 2009} \\
    \vspace{ -2 mm}	
    \begin{list2}
	\item Upgraded ROV platform for a successful ground-floor and water sampling project.
	\item Optimized underwater cabled digital video transmission and contributed to ReCON software development.
    \end{list2}\vspace{-2mm}

    \textbf{National Underwater Research Center} \hfill Research Assistant \\ 
	University of Connecticut \hfill \textsl{Jun. 2008 -- Feb. 2009} \\
    \vspace{ -2 mm}	
    \begin{list2}
	\item Assisted with the design, implementation, and operation of the Kraken2 remote observation vehicle.
	\item Implemented SNR reduction techniques for multiple NTSC video streams over a noisy medium.
	\item Served as main pilot and engineer for NOAA's Thunder Bay Sinkhole Project. 
    \end{list2}\vspace{-2mm}

   \pagebreak

    \textbf{Great Lakes Environmental Research Laboratory } \hfill  Electrical Engineer \\ 
	National Oceanic and Atmospheric Administration \hfill \textsl{May 2007 -- Sept. 2007; Jan. 2008 -- Jun. 2008}  \\
    \vspace{ -2 mm}	
    \begin{list2}
	\item Collaborated with Monterey Bay Aquarium Research Institute researchers to successfully implement a testbed for emerging 	observing systems software.
	\item Extracted and corrected biological backscatter information from acoustics data to quantify zooplankton vertical distribution and 	their relation to environmental factors in the Great Lakes.
    \end{list2}\vspace{-2mm}

    \textbf{Great Lakes Environmental Research Laboratory } \hfill Marine Instrumentation Engineer  \\ 
	National Oceanic and Atmospheric Administration \hfill \textsl{May 2006 -- Sept. 2006} \\
    \vspace{ -2 mm}	
    \begin{list2}
	\item Successfully automated the data retrieval process from buoy instrumentation.
	\item Developed an instrument platform to support two analog fluorometers for \textit{in situ} sampling.
    \end{list2}\vspace{-2mm}

        %__________________________________________________________________________________________________________________
    % Professional Activities
    \section{\mysidestyle Professional} 

    IEEE member of \textsl{Robotics and Automation} and \textsl{Oceanic Engineering} Societies  
	    
	\vspace{-4mm}
    %__________________________________________________________________________________________________________________
    %Skills
    \section{\mysidestyle Skills} 

    Java, Python, C/C++, Google Protobufs, Matlab, \LaTeXe, Maple, Mathematica, Bash, HTML, CSS, JIRA, Git, SVN, XFRACAS, Microsoft Office Suite

%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF

